MSF_Groupwork-NBA_shotlog

### 2016-10-09 MSFGroupwork-NBAHotHand.Rmd
Added columns for names of HOME and AWAY teams

@@

df[,"W"] <- as.numeric(df[,"W"])

>>>>

##Installing packages
```{r}
install.packages('reshape')

@@

df[,"W"] <- as.numeric(df[,"W"])
```

```{r}
#adding columns for names of 'home' and 'away' teams
df[,"MATCHUP"] <- as.character(df[,"MATCHUP"])

for (i in 1:nrow(df)) {
  df$HOME_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[5]
  df$AWAY_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[7]
}
```

```{r}
#combining columns for the analysis
library(reshape)
```
